Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-10-13 thesis/paper_draft.qmd
changed radar plot to include Base

```{r library}
library(ggplot2)
library(patchwork)
library(dplyr)
library(tidyr)
library(fable)
library(fabletools)
library(feasts)
library(tsibble)
library(lubridate)
library(knitr)
library(kableExtra)
library(stringr)
library(forcats)

@@

plot_uniscore <- function(score_label, title) {
  tourism_uniscores %>%
    filter(rule == score_label) %>%
    group_by(family, model_label, pc_k, iter) %>%
    summarise(
      score = mean(score),
      base_score = mean(base_score),
      pct_change = (base_score - score) / base_score * 100,
      .groups = "drop_last"
    ) %>%
    ungroup() %>%
    group_by(family, model_label, pc_k) %>%
    summarise(
      pct_change_avg = pmin(mean(pct_change), 10),   # cap at 10
      capped = as.integer(pct_change_avg >= 10),
      .groups = "drop"
    ) %>%
    filter(model_label != "Base", model_label != "OLS-S") %>%
    mutate(pc_k = ifelse(is.na(pc_k), "0", as.character(pc_k))) %>%
    # ggplot
    ggplot(aes(x = model_label, y = pct_change_avg,
              fill = family, alpha = pc_k)) +
      geom_col(color = "black", size = 0.5) +
      # geom_text(aes(label = ifelse(capped == 1, "> 10%", "")), vjust = -0.5) +
      recon_fill_scale +
      scale_alpha_manual(values = c("0" = 1, "1" = 0.6, "2" = 0.3), guide = "none") +
      labs(
        x = " ", y = " ",
        title = title
      ) +
      theme_minimal(base_size = 12) +
      theme(axis.text.x = element_text(angle = 25, hjust = 0.6)) +
      guides(fill = "none")
}

@@

```{r}
#| label: fig-tourism-radar
#| fig.height: 8
#| fig.width: 8
#| out.width: "90%"
#| fig-cap: "Radar plot of relative improvements in probabilistic scores (Winkler 80, Winkler 95, CRPS, Energy) over the base forecasts. The scores are scaled to a range of 0 to 100, with larger values indicating better performance. The outermost polygon represents the best possible score (100) and the innermost polygon represents the worst possible score (0). Only the top 5 models are shown."

# a radar plot of 5 top models based on probabilistic scores (Winkler 80, 95, CRPS, Energy) scaled to 0-100 
par(mfrow=c(1,1), mar=c(0,0,0,0))
tourism_plots$radar
```

The summary radar graph in @fig-tourism-radar consolidates these findings: among the selected MinT models by probabilistic criteria, *MinT-N(PC1)* (the yellow polygon) clearly leads across CRPS, W80, W95, and Energy, extending the improvements seen in the single-metric panels.

>>>>

```{r library}
library(ggplot2)
library(patchwork)
library(dplyr)
library(tidyr)
library(fable)
library(fabletools)
library(feasts)
library(tsibble)
library(lubridate)
library(knitr)
library(kableExtra)
library(stringr)
library(forcats)
library(tibble)
library(fmsb)

@@

plot_uniscore <- function(score_label, title) {
  tourism_uniscores %>%
    filter(rule == score_label) %>%
    group_by(family, model_label, pc_k, iter) %>%
    summarise(
      score = mean(score),
      base_score = mean(base_score),
      pct_change = (base_score - score) / base_score * 100, # positive indicate decrease in score
      .groups = "drop_last"
    ) %>%
    ungroup() %>%
    group_by(family, model_label, pc_k) %>%
    summarise(
      pct_change_avg = pmin(mean(pct_change), 10),   # cap at 10
      capped = as.integer(pct_change_avg >= 10),
      .groups = "drop"
    ) %>%
    filter(model_label != "Base", model_label != "OLS-S") %>%
    mutate(pc_k = ifelse(is.na(pc_k), "0", as.character(pc_k))) %>%
    # ggplot
    ggplot(aes(x = model_label, y = pct_change_avg,
              fill = family, alpha = pc_k)) +
      geom_col(color = "black", size = 0.5) +
      # geom_text(aes(label = ifelse(capped == 1, "> 10%", "")), vjust = -0.5) +
      recon_fill_scale +
      scale_alpha_manual(values = c("0" = 1, "1" = 0.6, "2" = 0.3), guide = "none") +
      labs(
        x = " ", y = " ",
        title = title
      ) +
      theme_minimal(base_size = 12) +
      theme(axis.text.x = element_text(angle = 25, hjust = 0.6)) +
      guides(fill = "none")
}

@@

```{r}
#| label: fig-tourism-radar
#| fig.height: 7
#| fig.width: 7
#| out.width: "70%"
#| fig-cap: "Radar plot of relative improvements in probabilistic scores (Winkler score at 80% and 95% intervals, CRPS, and Energy) over the base forecasts. The scores are scaled to a range of 0 to 100, with larger values indicating better performance. The outermost polygon represents the best possible score (100) and the innermost polygon represents the worst possible score (0). Only the top 4 MinT approaches are shown (with the base model)."

# a radar plot of 5 top models based on probabilistic scores (Winkler 80, 95, CRPS, Energy) scaled to 0-100 
par(mfrow=c(1,1), mar=c(1,2,1,2))
plot_radar(tourism_uniscores, tourism_energy)
```

The summary radar graph in @fig-tourism-radar consolidates these findings: among the selected MinT models by probabilistic criteria, *MinT-N(PC1)* (the yellow polygon) clearly leads across CRPS, Winkler score at 80% and 95% intervals, and Energy, extending the improvements seen in the single-metric panels. Except for the Winkler score at 95% interval, all MinT variants outperform the base forecasts.
